---
title: "Nepal Input Output Tables"
format: pdf
editor: visual
execute: 
  echo: false
  warning: false

---

## Nepal Input Output Tables




```{r init}
library(dplyr)
library(ggplot2)
library(purrr)
library(readxl)

```


```{r}


# set directory paths to retrieve stored data or files
dat_dir <- "C:/users/hello/rprojects/upwork"

.path <- "~/data/institutions/adb/nep_iot.xlsx"

iot13 <- read_excel(.path, range = "2013!A7:AL42")

names_iot3 <- pull(iot13,1)
iot13 <- select(iot13, -c(2,3))
# names(iot13) <- c("industry", names_iot3)

```

```{r}
# m <- iot13[,-1] %>% unlist() %>% unname()
# 
# m2 <- matrix(m, nrow = 35, dimnames = list(names_iot3, names_iot3))
# 
# actual_inv <- solve(diag(nrow(m2)) - m2) `
```


```{r}

# The following code snippet transforms data set into matrix form and
## finds the necessary inverse

# get the names of the industry (previously stored)
industry_names <- readRDS(paste0(dat_dir,"/data/institutes/adb/nepal_iot.RDS"))

# Computing forward linkages
.path <- "~/data/institutions/adb/nep_iot.xlsx"

# Get the coefficients matrix. We can calculate inverse matrix from this

coeff_matrix <- function(year,type = "input"){
  
  if(type == "input"){
                   m <- read_excel(.path, range = paste0(year,"!A8:AL42"), 
                          col_names = FALSE)
  } else if(type == "output"){
                   m <- read_excel(.path, range = paste0(year,"!A43:AL77"), 
                          col_names = FALSE)
  }

  
  m <- select(m,-c(2,3)) # remove irrelevant columns
  m <- unname(unlist(m[,-1])) # remove names and convert into a list of numbers only
  
  (m <- matrix(m, nrow = 35, dimnames = list(industry_names,industry_names)))

}


inverse_matrix <- function(year,type = "input"){
  
  m <- coeff_matrix(year = year, type = type)
  solve(diag(nrow(m))-m)
  
}

```

## Forward linkages

Forward linkages capture the partial effect that an industry has on other industries. 

As in the case of backward linkages, we can calculate both direct and total forward linkages. Direct forward linkage of sector *i* is given by the sum of the elements of the *ith* row in the output coefficients matrix $B$. 

Total forward linkage captures both direct and indirect effects and is given by the row sums of the output inverse matrix $G = (I-B)^{-1}$ where $I$ is the $35 X 35$ identity matrix and $B$ is the output coefficients matrix. 

```{r}


linkage <- function(year, method, type){
  
  if(type == "forward") {
    type = "output"
  } else if(type == "backward"){
    type = "input"
  } else stop("Incorrect type!")
    
  
  if(method == "direct"){
    
     A <- rowSums(coeff_matrix(year = year, type = type))

  } else {
    
    if(method == "total"){
      
      A <- rowSums(inverse_matrix(year = year, type = type))
      
    } else stop("`method` may only be either `direct` or `total`")
  }
  
    as_tibble(cbind(industry = names(A), value = unname(A))) |>
     mutate(value = as.numeric(value),
             normalized_value = value/sum(value))

}

linkage(2012,"direct","forward")
```
`
```{r}

years <- excel_sheets(.path)[-1]
purrr::map(years, ~linkage(.x,"total","forward")) |> 
  set_names(years) |>
  bind_rows(.id = "year") -> d
```

